---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%"
)
```

# mapiso

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable
state and is being actively
developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)

[![R-CMD-check](https://github.com/rCarto/mapiso/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rCarto/mapiso/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `mapiso` is to create isopleth polygon sf object from raster or regular grids.


## Installation

You can install the development version of `mapiso` from
GitHub with:

``` r
remotes::install_github("rcarto/mapiso")
```


## Usage


### Raster

```{r raster}
library(mapiso)
library(terra)
library(mapsf)
r <- rast("inst/tif/elevation.tif")
isor <- mapiso(x = r)
mf_theme(mar = c(0, 0, 0, 0))
mf_raster(r)
mf_map(isor, col = NA, add = TRUE)
```

### sf regular grid

```{r sf}
library(mapiso)
library(sf)
library(mapsf)
s <- st_read("inst/gpkg/elevation.gpkg", quiet = TRUE)
bks <-c(98,100, 150, 200, 250, 300, 350, 400, 412.6) 
isos <- mapiso(x = s, var = "elevation", breaks = bks)
mf_map(isos, "isomin", "choro", breaks = bks, leg_title = "elevation")
```

### data.frame


```{r data.frame}
library(mapiso)
library(mapsf)
d <- read.csv("inst/csv/elevation.csv")
head(d)
isod <- mapiso(x = d, var = 'elevation', coords = c('x', 'y'), crs = 'epsg:2154')
bks <- unique(c(isod$isomin, isod$isomax))
mf_map(isod, "isomin", "choro", breaks = bks, leg_title = "elevation")
```



## Community Guidelines

One can contribute to the package through [pull
requests](https://github.com/rcarto/mapiso) and report issues or
ask questions [here](https://github.com/rcarto/mapiso/issues).  
This project uses [conventional
commits](https://www.conventionalcommits.org/en/v1.0.0-beta.3/) and
[semantic versioning](https://semver.org/).
